Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-09-15 documents/TriangleScenarioArXiv/ts.tex
Final edits to the paper

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In scenarios where all parties share a common resource, these non-classical correlations are also known as non-local correlations. Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. This provides the first robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).

@@

    \Cref{sec:main_appendix} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive the causal compatibility inequalities for the Triangle structure which admit violation by quantum-accessible distributions.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by classical correlations (compatible with some classical causal structure) are also all satisfied by quantum correlations (generated by the quantumified causal structure in which latent variables are replaced with shared entanglement) \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:main_appendix} discusses the Inflation Technique as applied in this work.

@@

    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A (B)$ determined by their individual measurement settings $S_A (S_B)$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}. The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$. Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
    %    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
    \begin{align}\label{eq:bellcompat}
     \prob \text{ is classically compatible with \cref{fig:bell_structure}} \quad\text{iff} \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
    \end{align}

@@

    Let us now contrast now the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement operators $M_{A|S_A}, M_{B|S_B}$ with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities (such as the CHSH inequality \cref{eq:CHSH_ineq_orig} reproduced below) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
    \[ \ba{\p A\p B | S_{A} = 0, S_{B} = 0} + \ba{\p A\p B | S_{A} = 0, S_{B} = 1} + \ba{\p A\p B | S_{A} = 1, S_{B} = 0} - \ba{\p A\p B | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \[ \prob \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\text{iff}\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,. \eq \label{eq:triangle_compatibility} \]
    By contrast, the quantum distribution of the Triangle structure are defined with substantially greater freedom, namely
    \[ \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]

@@

    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicallity are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new polynomial causal compatibility inequalities for the Triangle structure. The inequalities of Ref. \cite{Inflation} are especially sensitive, in that they expose a distribution which had previously evaded detection as incompatible with the Triangle structure as assessed by all formerly known constraints.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. In \Cref{sec:preliminary_research} we report on attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    As first realized by \citet{Fritz_2012}, one may construct quantum distributions incompatible with the Triangle structure by recasting quantum distributions incompatible with the familiar Bell structure into a settings-free tripartite format. To explain, imagine rearranging the Triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} so that it morely closely resembles the Bell structure of \cref{fig:bell_structure}. Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that $S_{A}, S_{B}$ are random variable representing the recorded measurement \emph{settings} in the Bell structure whereas those $S_{A}, S_{B}$ are \emph{latent} variables in in the Triangle structure, which get reported as \textit{auxiliary outcomes} for Alice and Bob.

@@

    The exemplifying quantum distribution corresponding to a recasting of a nonclassical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}. In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$. It is convenient to represent the outcomes using two binary digits, $\bc{00,01,10,11}$. Explicitly, $\prob[\fritz]$ can be written as:

@@

    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
    The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block. When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by (i.e. perfectly correlated with) the outcome of $\p C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits $\p A_l$ and $\p B_l$ emulate the measurement settings $S_{\p A}$ and $S_{\p B}$, whereas the right-hand bits $\p A_r$ and $\p B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure of \cref{fig:bell_structure}. Critically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.

@@

    Consequently, it is possible to define the correlation $\ba{\p A_r \p B_r}$ between the right-hand bits of $\p A$ and $\p B$:
    \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]

@@

         \p A_l\leftarrow S_{A}\,,\quad
         \p B_l\leftarrow S_{B}\,,\quad
         \p C_l\leftarrow S_{A}\,,\quad
         \p C_r\leftarrow S_{B}\,.

@@

    As an example, the famous CHSH inequality~\cite{CHSH_Original} per \cref{eq:CHSH_ineq_orig} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]

@@

    It is important to understand the domain in which Fritz's proof of incompatibility is valid.  %the details of which can found in the original work~\cite{Fritz_2012}. Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists
    The proof relies on the perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$. For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not? At what point does the resultant distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

    Plainly $\prob[\fritz]$ is a valid but \textit{manufactured} example. The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics. The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}. Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In structures where all parties share a common resource, these non-classical correlations are also known as non-local correlations. Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. This provides the first robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).

@@

    \Cref{sec:inflation_technique_summary} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented in \Cref{sec:inflation_technique_summary} is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive the causal compatibility inequalities for the Triangle structure which admit violation by quantum-accessible distributions.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by classical correlations (compatible with some classical causal structure) are also all satisfied by quantum correlations (generated by the quantumified causal structure in which latent variables are replaced with shared entanglement) \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.

@@

    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A (B)$ determined by their individual measurement settings $S_A (S_B)$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}. The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$. Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[A|S_A,\la]$ is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
    %    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
    \begin{align}\label{eq:bellcompat}
     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
    \end{align}

@@

    Let us now contrast now the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,. \eq \label{eq:triangle_compatibility} \]
    By contrast, the quantum realization of the Triangle structure are defined with substantially greater freedom, namely
    \[ \prob[ABC] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]

@@

    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicallity are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of Ref. \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. In \Cref{sec:preliminary_research} we report on attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    As first realized by \citet{Fritz_2012}, one may construct quantum distributions incompatible with the Triangle structure by recasting quantum distributions incompatible with the familiar Bell structure into a settings-free tripartite format. To explain, imagine rearranging the Triangle structure into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} so that it closely resembles the Bell structure (\cref{fig:bell_structure}). Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that $S_{A}, S_{B}$ are random variable representing the recorded measurement \emph{settings} in the Bell structure whereas those $S_{A}, S_{B}$ are \emph{latent} variables in in the Triangle structure, which get reported as \textit{auxiliary outcomes} for Alice and Bob.

@@

    The exemplifying quantum distribution corresponding to a recasting of a non-classical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}. In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$. It is convenient to represent the outcomes using two binary digits, $\bc{00,01,10,11}$. Explicitly, $\prob[\fritz]$ can be written as:

@@

    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
    The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block. When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by (i.e. perfectly correlated with) the outcome of $C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded}, the left-hand bits $A_l$ and $B_l$ emulate the measurement settings $S_{A}$ and $S_{B}$, whereas the right-hand bits $A_r$ and $B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure (\cref{fig:bell_structure}). Critically, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.

@@

    Consequently, it is possible to define the correlation $\ba{A_r B_r}$ between the right-hand bits of $A$ and $B$:
    \[ \ba{A_r B_r} = \prob[A_r B_r][00] + \prob[A_r B_r][11] - \prob[A_r B_r][01] - \prob[A_r B_r][10] \eq \label{eq:right_bit_correlations} \]

@@

        A_l\leftarrow S_{A}\,,\quad
        B_l\leftarrow S_{B}\,,\quad
        C_l\leftarrow S_{A}\,,\quad
        C_r\leftarrow S_{B}\,.
        \eq \label{eq:fritz_relabelling}

@@

    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
    \[ \ba{A_r B_r|C = 00} + \ba{A_r B_r|C = 01} + \ba{A_r B_r|C = 10} - \ba{A_r B_r|C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]

@@

    It is important to understand the domain in which Fritz's proof of incompatibility is valid.  %the details of which can found in the original work~\cite{Fritz_2012}. Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists
    The proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$. For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not? At what point does the resultant distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

    Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example. The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of non-classical resources made accessible by quantum mechanics. The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}. Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:
